On Designing Collusion-Resistant Incentive Mechanisms for Mobile Crowdsensing Systems

### 2015-12-26 response.tex

\question Some important related literatures are missing.
\begin{solution}
Previously I give few citations to the existing works based on auction theory. Now I have given some of them: DiPalantino's and Liu's all-pay auctions, Feng's TRAC, etc.
\end{solution}

\section{Reviewer 2}
\question In Section VII, the simulations demonstrate that the authors’ crowdsensing incentive mechanism can achieve group strategyproof and n-truthful equilibrium simultaneously. However, if we do not consider the collusion attack problem, how are about the performance of the proposed crowdsensing incentive mechanism compared to other existing ones? The authors did not discuss it.  
\begin{solution}
Previously the experiment design is not good, since to show the security properties such as achieving group strategyproofness, one has to do it in theory rigorously, rather than simulations. Now I have decided to rebuild the experiments and compare the performance of our mechanism to other works such as Koutsopoulos's. I have considered three performance measurements: running time, budget utilization ratio and finished sensing task ratio. These three measurements can verify our mechanism is efficient, budget feasible and can finish most of the given tasks appropriately. Hence I have rewritten the experimental section. Now the performance question proposed by this reviewer can be answered, while the rigor of (group) strategyproofness has been achieved by theoretical reasoning.
\end{solution}

\question In Page 1, the authors say “But like other penetration analysis, there is no guarantee of guard against unexamined cases”. However, in Page 9, they conclude that the proposed crowdsensing incentive mechanism can resist any collusion attack. So, if there exists an unexamined collusion attack except those ones in the paper, can the  crowdsensing incentive mechanism be against it?  which is not clear in the paper.
\begin{solution}
Since we have eliminate the possibility of any collusion attack even with profit trading in theory rigorously, it is safe to say that our mechanism can resist any collusion attack in any form. 
We have added more discussions regarding this point in Section IX.
\end{solution}

@@

\question In Page 4 Section IV, “e” should be modified to “we”.
\begin{solution}
This typo has been fixed.
\end{solution}

\question In Page 2, the caption of Table 1  should be on the top of itself.
\begin{solution}
This problem has been fixed.
\end{solution}

\section{Reviewer 3}
\question The limitation of this paper is that it only studies two specific types of crowdsensing systems, where the user's participation level is measured by sensing time and the number of sensing tasks respectively. There are also other crowdsensing systems, for example, users can also submit the set of crowdsensing tasks to perform with their cost.
\begin{solution}
Even though our models are not the unique solutions to crowdsensing game, they are quite general and typical. They capture the most important features of crowdsensing: payment and workload (sensing time of each user). The equation $u = p - \kappa t$ should reflect most crowdsensing games. If some users cannot participate due to certain restrictions, they can simply quit. All the participating users can give a game which is convenient to research. On the other hand, many restrictions such as different sets of tasks for different users are difficult to define. Thus in this paper we decide to focus on the most general and typical crowdsensing game model in existing works. 
I have added more discussions about this point in Section III.A.
\end{solution}

\question For the first type of crowdsensing model, where the user's participation level is measured by sensing time, only a strategyproof, but not group strategyproof, incentive mechanism is described.
\begin{solution}
Our main result, Theorem 1, has given the condition which strategyproof game can also be group strategyproof. That is, the PDG must be acyclic. This is a quite general result, which can spawn many different constructions.
\end{solution}

### 2015-12-26 response.tex

\question For the first type of crowdsensing model, where the user's participation level is measured by sensing time, only a strategyproof, but not group strategyproof, incentive mechanism is described.
\begin{solution}
Our main result, Theorem 1, has given the condition which strategyproof game can also be group strategyproof. That is, the PDG must be acyclic. This is a quite general result, which can spawn many different constructions.
\end{solution}

\question Typos: 
In Section I, ``For another group of typical crowdsensing game'', ``When the possibility that colluding nodes can trade profit among them''
In Section II.B, ``a equilibrium''
In Section III, ``We also present an example to present''
In Section IV, ``e leverage...''
\begin{solution}
All the typos have been fixed. That is, 
In Section I, ``For another group of typical crowdsensing games'', ``When it is possible that colluding nodes can trade profit among them''
In Section II.B, ``an equilibrium''
In Section III, ``We also present an example to illustrate''
In Section IV, ``we leverage...''
\end{solution}

\section{Reviewer 4}
\question My major concern is that the paper is more of a kind of reverse engineering. The main architecture is similar to those in references [14][17][20]. The analysis tools are almost directly applied to the crowdsensing platform, without addressing the unique features of crowdsensing platform, which is different from other scenarios. My detailed comments are as follows:
\begin{solution}
We have only researched one typical game model. If one considers the very practical crowdsensing systems in the real world, our contribution cannot answer every problem. However, we have offered a graph based analysis method, which I think should be interesting and may give inspiration to other problems in crowdsensing game.
\end{solution}

\question First, the authors should justify the motivation for users to collude. Normally, crowdsensing users may not be aware of the identity of other users. Collusion is very hard to be conducted when the cost of coordinating colluders’ actions is high. The author did mention that one person may own multiple devices and collude among those devices. But a user may own 2-3 devices, while the entire user population may be on the scale of thousand. 
\begin{solution}
It is good to add more discussions on the collusion size and our results. Firstly, it is usually difficult to guarantee the upper bound of collusion size, since the adversarial always try to hide such information. Secondly, if such an upper bound can be guaranteed, then any strategyproof mechanism can be group strategyproof by satisfying a much weaker condition, i.e., the size of smallest cycles in the PDG is larger than the upper bound of collusion size. 
We have added more discussions in Sections I and IV. Corollary 1 has been added to reflect the upper bound of collusion size and our results. The new text has been highlighted in blue.
\end{solution}

\question I want to know whether the platform utility will be affected by adopting the proposed collusion-resistant mechanism. Equation (2) gives the platform utility, but afterwards there is no theoretical or numerical analysis on the platform utility. The objective of the platform operator may be more focused on utility maximization rather than eliminating all the collusions.
\begin{solution}
Note that the platform utility is never mentioned in this version. Therefore, I decide to remove all the platform utility. Now we assume the platform are always willing to conduct the crowdsensing game, since the budget is given and we can guarantee that our mechanism is budget feasible. Then the incentive for the platform can be related to the budget minus all the payments.
\end{solution}

\question Equation (3) and (4) needs clearer explanation. Notations $s*_S$ and $s*_{\overline{S}}$ should be defined. It should be clearly stated that $s*_S$ is the strategy profile of the users in set $S$, and $\overline{S}$ is the complementary set of $S$. 
\begin{solution}
I have given discussions about the notations. The explanations are also added in the symbol table. All the new entries are highlighted in blue.
\end{solution}

\question It is strange that the required sensing time, computed by the crowdsensing platform, only depends on the reported cost of users, just for the sake of collusion-resistance. The required sensing time is associated with the sensing task itself. I wonder if the collusion-resistant incentive mechanism can only manipulate the payment $p_i$ rather than the required sensing time $t_i$. 
\begin{solution}
If one assumes the platform does not return $t_i$ to each user, the resulted model is significantly different from ours. The difficulty to achieve any collusion resistance is that the platform has no idea about the exact cost unit of each user. To be fair, the platform can only give payment proportionally to each user's contribution. Then for the users with low cost unit, she can do the tasks as many as she can, and there is no maximum utility for her. Clearly for this case there is no equilibrium. On the other hand, our model has received extensive research in exsiting works. 
The general game model in this paper was proposed by Koutsopoulos in INFOCOM. Yang et al have given another similar model in MOBICOM, but the platform knows the cost unit of each user exactly. Hence I think it is still worth researching on this model. However, expanding the current results by changing the assumptions is good and requires further future work.
\end{solution}

\question The evaluation setting is very confusing. I don’t understanding why “a colluded user i’s cost unit is 1.0, and the perturbation size is 2.0. Then this user i has probability of 25\% to claim $s_i$ = 0,01, and 75\% to claim a strategy larger than 0.01” , where did the figures 25\% and 75\% come from? Can it be 10\% and 90\%? Also, if some users collude, they will choose the optimal reported cost rather than randomly choosing a cost to report, which may hurt their utility.  So I don’t think the results in Fig. 5---10 are valid. Also, the utility comparison of the platform operator under non-collusion-resistant and collusion-resistant mechanisms is wanted. 
\begin{solution}
I think in previous versions, the experiment design is not good, since if one wants to show security properties such as group strategyproofness, the only way is to do it in theory rigorously. Since we have given the conditions of group strategyproofness and profit trading resistance, it should be safe to say our mechanism achieves the desired goals and there is no need to ``verify'' by using experimental results.

For experiments, I think it should be much better if we focus on the performance of our mechanism, e.g., running time, utilization of the budget, finishing ratio of the available sensing tasks, etc. Thus in this version, I have rewritten the experimental part. I have redone all the experiments, and given all the results of performance. Hope by doing this our experimental part can make more sense. 
\end{solution}

\question Typos, line 50, page 4, left column, “e leverage”. Line 10, page 5, left column, PDG is not defined.
\begin{solution}
The typo has been fixed. 
The definition of PDF has been push forwarded into Section IV for a better presentation.
\end{solution}
\end{questions}
\end{document}

### 2015-12-26 techreport.tex
Address reviewer 4's.

{\color{black}
\section{System Models and Problem Formulation}
\label{sec:PFSM}
{\color{black}
In this section, we formalize a popular type of crowdsensing scenarios, and then describe a typical strategyproof incentive mechanism. We also present an example to illustrate how collusion attack can make this incentive mechanism fail. %At last we will discuss the assumptions of discrete crowdsensing game.
%We will also discuss the privacy preserving problem against traffic analysis and timing attacks.
}

@@

\subsection{An Example of Collusion on Strategyproof crowdsensing Game}
Unfortunately, a strategyproof incentive mechanism is usually not strong enough to resist collusion rigorously. 
{\color{black}
For example, suppose a game has two users $i,j$ s.t. $\kappa_i = \kappa_j = 1$. Given the user strategies $s_i$ and $s_j$, for user $i$ let its sensing time be $t_i(s_i, s_j)=s_j\mathrm{e}^{-s_i}$ and let its payment be $$p_i(s_i, s_j)=s_it_i(s_i, s_j)+\int_{s_i}^{+\infty}t_i(s, s_j)\mathrm{d}s=(s_i+1)s_j\mathrm{e}^{-s_i}.$$ The case of user $j$ is analogous. Thus the user utilities are 
\begin{equation}
\begin{aligned}
u_i(s_i,s_j)=&p_i(s_i, s_j)-\kappa_it_i(s_i, s_j) \\
=&(s_i+1)s_j\mathrm{e}^{-s_i} - 1\times s_j\mathrm{e}^{-s_i} \\
=&s_js_i\mathrm{e}^{-s_i},\\
\end{aligned}
\end{equation}
and similarly $u_j(s_i,s_j)=s_is_j\mathrm{e}^{-s_j}$. 
}
It can be shown this game is strategyproof. If both $i,j$ act truthfully, we have $u_i(1,1)=u_j(1,1)=1/e$, and each utility is maximized by fixing the other strategy to be 1. However, if both $i,j$ declare their cost units as 1.1, we have $u_i(1.1,1.1)=u_j(1.1,1.1)>0.4>1/e$ and thus $i,j$ can together conduct a valid collusion to achieve higher utilities. It is worth researching the criteria that any strategyproof game must satisfy in order to be collusion resistant. %In the following sections, we will show the quantitative relation between collusion and the parametric dependencies. The conception of parametric dependency is given by Definition \ref{def:pd}.
}

>>>>

{\color{black}
\section{System Models and Problem Formulation}
\label{sec:PFSM}
In this section, we formalize a popular type of crowdsensing scenarios, and then describe a typical strategyproof incentive mechanism. We also present an example to illustrate how collusion attack can make this incentive mechanism fail. %At last we will discuss the assumptions of discrete crowdsensing game.
%We will also discuss the privacy preserving problem against traffic analysis and timing attacks.

@@

{\color{blue}
Note that the mechanism above captures the two most important characteristics of crowdsensing: workload (sensing time) and payment. Practical crowdsensing game may require additional restrictions. For example, each user can submit a set of sensing tasks, or the tasks are not uniform on workload, etc. Most of these restrictions are not well defined, i.e., vary among different games. In this paper, we focus on the most general typical model as above.
}

\subsection{An Example of Collusion on Strategyproof Crowdsensing Game}
Unfortunately, a strategyproof incentive mechanism is usually not strong enough to resist collusion rigorously. 
{\color{black}
For example, suppose a game has two users $i,j$ s.t. $\kappa_i = \kappa_j = 1$. Given the user strategies $s_i$ and $s_j$, for user $i$ let its sensing time be $t_i(s_i, s_j)=s_j\mathrm{e}^{-s_i}$ and let its payment be $$p_i(s_i, s_j)=s_it_i(s_i, s_j)+\int_{s_i}^{+\infty}t_i(s, s_j)\mathrm{d}s=(s_i+1)s_j\mathrm{e}^{-s_i}.$$ The case of user $j$ is analogous. Thus the user utilities are 
\begin{equation}
\begin{aligned}
u_i(s_i,s_j)=&p_i(s_i, s_j)-\kappa_it_i(s_i, s_j) \\
=&(s_i+1)s_j\mathrm{e}^{-s_i} - 1\times s_j\mathrm{e}^{-s_i} \\
=&s_js_i\mathrm{e}^{-s_i},\\
\end{aligned}
\end{equation}
and similarly $u_j(s_i,s_j)=s_is_j\mathrm{e}^{-s_j}$. 
}
It can be shown this game is strategyproof. If both $i,j$ act truthfully, we have $u_i(1,1)=u_j(1,1)=1/e$, and each utility is maximized by fixing the other strategy to be 1. However, if both $i,j$ declare their cost units as 1.1, we have $u_i(1.1,1.1)=u_j(1.1,1.1)>0.4>1/e$ and thus $i,j$ can together conduct a valid collusion to achieve higher utilities. It is worth researching the criteria that any strategyproof game must satisfy in order to be collusion resistant. %In the following sections, we will show the quantitative relation between collusion and the parametric dependencies. The conception of parametric dependency is given by Definition \ref{def:pd}.
}
